Adopting agile in the large: motivations, success factors and challenges

### 2014-05-04 journal/article.tex
Improvements

A condition hindering the transformation was that old commitments still needed
to be tended to even though the organization was being restructured.
Some organizations started their agile journey in a state where people were
overcommitted, but it was later realized that overloaded people will not be able
to learn new ways of working and changing their behavior [P37, P42]. Cowan [P11]
describes how time was allocated for tending to old commitments. However, even
when extra work was prepared for people with specific expertise became
overloaded. After time it was realized that overcommitment must be reduced by
allowing to shift excess work for later time [P11]. In another case management
forced people to remain committed to firm deadlines, even midst in the
organizational transformation. The engagement in old commitments and tasks
resulted in ignoring new practices introduced by agile, and eventually the agile
method was breaking down [P21].

@@

% Lack of resources

@@

>>>>

A condition hindering the transformation was that old commitments still needed
to be tended to even though the organization was being restructured.
Some organizations started their agile journey in a state where people were
overcommitted, but it was later realized that overloaded people will not be able
to learn new ways of working and changing their behavior [P37, P42]. Cowan [P11]
describes how time was allocated for tending to old commitments. However, even
when there was preparation for extra work people with specific expertise became
overloaded. After time it was realized that overcommitment must be reduced by
allowing to shift excess work for later time [P11]. In another case management
forced people to remain committed to firm deadlines, even midst in the
organizational transformation. The engagement in old commitments and tasks
resulted in ignoring new practices introduced by agile, and eventually the agile
method was breaking down [P21]. Spayd [P49] also describes how senior management 
pressed teams to deliver what the customer had been promised, regardless of what
the current velocity of development predicted.

@@

% Lack of training and coaching

@@

% Add quote?
% * No coaching --> Applying techniques improperly --> Damage
% [P9]
% Without proper coaching however, the success of these informal teams met with
% mixed results over the longer term.  In retrospect, many of these teams did
% damage to themselves by improperly applying Agile techniques, particularly when
% command and control mechanisms were still in place.
